Co-citations in context

### 2019-09-11 cocit_r_v2.tex
resetting revisions

>>>>

\section{Reviews}
\subsection{Reviewer 1}

\emph{The revised manuscript is much improved, and the specific comments to both reviews were very helpful. Overall, the authors have addressed all of the issues I’ve raised satisfactorily. The paper is important as a critique to Uzzi.
The paper does not claim to present an alternative (better) way to identify innovative papers.  But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
In my second reading, I did realize one additional flaw that I would like the authors to address- upon the editor’s discretion.  It looks like the study had a low threshold (just two references) for including papers in their studies. And we know that citation impact is correlated with the number of references. Is it possible that the signals they (or Uzzi) get for ‘innovative’ or ‘conforming’ are dependent on the number of references? This can be easily checked (a simple table of \# of references and likelihood of a signal of conformity or innovativeness) should be done. I suspect you won’t get any signal for papers with fewer than 5 references (how can one really assess either concept with such a small number?).  But with 10 or more references- I’m quite comfortable with conclusions about impact being based on conformity and innovativeness. They may also find, when applying a reference threshold (such as 10) that they get different results.}

\begin{itemize}
\item Conventionality and Innovativeness are part of the framework developed by Uzzi. We neither challenge nor embrace the framework but simply use it a read out. The reviewer is holding us responsible for Uzzi's construct.
\item We provide quantitative data addressing the reference count issue.
\end{itemize}

\subsection{Reviewer 2}

\emph{I would like to thank the authors for the revision.  However, I am afraid the revision has not sufficiently addressed my concerns. First, thanks for clarifying the reference shuffling.  Let’s say Pub A has a reference B, A is in discipline X and B in discipline Y.  I initially thought the local network approach swaps B with another reference which is also in discipline Y.  The authors actually did was to swap B with another reference from another paper which is in discipline X.  Is that correct?  The authors have clarified it in the paper, but I think it still needs to improved, maybe provide some illustrative examples.  Although my initial comment was because of misunderstanding the method, the underlying argument still holds.  It is still unclear whether global or discipline-specific novelty is more appropriate.  For example, bibliometrics papers cite a lot of mathematics paper, so in the pool of references cited by bibliometrics, combinations between bibliometrics and mathematics are very common.  However, mathematics do not cite bibliometrics so much, then combinations between bibliometrices and mathematics seems rather unusual when examining the mathematics.  I can see arguments supporting both the global and local approaches.  I do not think this paper can get away with it without clarifying the conceptualization. Second, the relationship between novelty/conventionality and citation impact itself does not seem to be a ground truth.  Using statistics about misspecification is based on a huge assumption, which needs to be made explicit and supported by conceptualization and theories.}

An irresponsible choice of words- `I do not think this paper can get away with it...' We are not trying to get away with anything!  Perhaps the reviewer confuses her/his own clumsy sophistry with our presentation? If so, it is most regrettable and we will strive to  ensure a distinction. Secondly, the reviewer's critique suffers from being somewhat incoherent. Even so....
\begin{itemize}
\item An illustration has been provided
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not
\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons
\end{itemize}
